Another paper with lots of text and fancy pictures

### 2023-12-11 paper.tex
Anisotropicity -> anisotropy: it seems these words means the same

\section{Results}
In this section we compute correlation functions along the plane $XY$ for 2- and
3-dimensional real samples. Table \ref{tab:summary} contains information about
these samples. Note that we compute surface correlation functions only for those
samples for which the criterion $C_{0.5} > 0.97$ holds (the sandstone and the
limestone). Images of the samples are on \cref{fig:samples}. On plots of
correlation functions we provide a family of curves with the first argument of
the correlation function being fixed. For two highly anisotropic samples (the
soil and the shale) we provide heatmaps of $S_3$ correlation function where
anisotropicity can be easily seen. These two samples was preliminary rotated by
$\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.

@@

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}. Anisotropicity of the both samples can be seen as a slower
decay of $S_3$ in one of the directions. Additionally, it can be observed that
elongated clusters of the void phase in the sample of soil are parallel to each
other and have a regular spacing about $50 \mu m$.

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropicity more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

@@

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropicity of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. A
direction of elongation for a $N$-dimensional image can be easily detected by
firstly evaluating a $N \times N$ covariance matrix for points belonging to the
phase of interest:
\begin{equation}
  C_{ij} = \sum_{x \in \left\{ \text{Coordinates of points in the
      phase of interest} \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
\end{equation}
and then decomposing $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
$\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation and
can be used to align the elongation with the axes (compare \cref{fig:aniso-unrot}
and \cref{fig:aniso-rot}).

>>>>

\section{Results}
In this section we compute correlation functions along the plane $XY$ for 2- and
3-dimensional real samples. Table \ref{tab:summary} contains information about
these samples. Note that we compute surface correlation functions only for those
samples for which the criterion $C_{0.5} > 0.97$ holds (the sandstone and the
limestone). Images of the samples are on \cref{fig:samples}. On plots of
correlation functions we provide a family of curves with the first argument of
the correlation function being fixed. For two highly anisotropic samples (the
soil and the shale) we provide heatmaps of $S_3$ correlation function where
anisotropy can be easily seen. These two samples was preliminary rotated by
$\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.

@@

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}. Anisotropy of the both samples can be seen as a slower
decay of $S_3$ in one of the directions. Additionally, it can be observed that
elongated clusters of the void phase in the sample of soil are parallel to each
other and have a regular spacing about $50 \mu m$.

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.45\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropy more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

@@

Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
rotations or trial triangles. It is sensitive to anisotropy of the medium
when it is stretched along one of the axes as shown in \cref{fig:aniso}. A
direction of elongation for a $N$-dimensional image can be easily detected by
firstly evaluating a $N \times N$ covariance matrix for points belonging to the
phase of interest:
\begin{equation}
  C_{ij} = \sum_{x \in \left\{ \text{Coordinates of points in the
      phase of interest} \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
\end{equation}
and then decomposing $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
$\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation and
can be used to align the elongation with the axes (compare \cref{fig:aniso-unrot}
and \cref{fig:aniso-rot}).
